KidsAIR: Main analysis

### 2021-06-09 intervention_questionnaire_summary.Rmd
PM analysis updates. Manuscript revisions from co-author comments.

# Summarize questionnaires for K99/R00 proposal
```{r}
kids_pwq_filter_summary <- kids_pwq_filter_clean %>% 
  filter(area == "WMT") %>% 
  filter(winter_id == 2) 
summary(kids_pwq_filter_summary)

kids_pwq_education_summary <- kids_pwq_education_clean %>% 
  filter(area == "WMT") %>% 
  filter(winter_id == 2) 
summary(kids_pwq_education_summary)

>>>>

# Summarize questionnaires for K99/R00 proposal
```{r}
kids_pwq_filter_summary <- kids_pwq_filter_clean %>% 
  filter(treatment_assigned == "Filter") %>% 
  select(area, winter_id, fuse, helpful, continuously) %>% 
  group_by(winter_id) %>% 
  mutate(winter_n = n()) %>% 
  group_by(winter_id, winter_n, helpful) %>% 
  count() %>% 
  mutate(var_perc = round(n/winter_n*100, digits = 1)) %>% 
  ungroup() %>% 
  select(winter_id, helpful, n, var_perc)
kids_pwq_filter_summary

kids_pwq_education_summary <- kids_pwq_education_clean %>% 
  select(area, winter_id, mmuse, mmhelpfulness,
         thuse, thhelpfulness, fsuse, fshelpfulness) %>% 
  group_by(winter_id) %>% 
  mutate(winter_n = n()) %>% 
  group_by(winter_id, winter_n, fshelpfulness) %>% 
  count() %>% 
  mutate(var_perc = round(n/winter_n*100, digits = 1)) %>% 
  ungroup() %>% 
  select(winter_id, fshelpfulness, n, var_perc)
kids_pwq_education_summary

### 2021-06-09 main_analysis_final.Rmd
PM analysis updates. Manuscript revisions from co-author comments.

---
title: 'KidsAIR: Main analysis'
author: "Ethan Walker"
date: "Updated 24 March 2021"
output: pdf_document
---

@@

```{r}
library(readxl)
library(naniar)
library(lubridate)
library(emmeans)
library(broom)
library(broom.mixed)
library(zoo)
library(lme4)
library(lmerTest)
library(mctest)
library(tidyverse)
library(knitr)
library(kableExtra)
library(MASS)
library(faraway)
library(DHARMa)
```

@@

analysis_data_winter1 <- read_rds(paste0(file_path, 
                                 "Output/kids_analysis_data_2obs_per_child.rds")) %>% 
  mutate(pm_mean_sampling_period_iqr = pm_mean_sampling_period/25,
         pm_mean_at_home_sampling_period_iqr = pm_at_home_sampling_period/25,
         pm_mean_at_home_sampling_period = pm_at_home_sampling_period,
         lrti_events_di_winter = as.factor(lrti_events_di_winter),
         child_age = factor(child_age, levels = c("< 1", "1+")),
         moisture_di = cut(moisture_closest, breaks = c(0, 11, 100),
                           labels = c("<11%", ">=11%")),
         stove_age_di = fct_collapse(stove_age_3level, 
                                     "0-5 years old" = "0-5 years old",
                                     "6+ years old" = c("6-15 years old", "16 + years old"),
                                     "Do not know" = "Do not know")) %>% 
  filter(person_time_at_risk_winter > 0) %>% 
  #filter(area == "WMT") %>% 
  filter(winter_id == 1)

@@

# Run primary model and print results
itt_results_int <<- glmer(lrti_events_di_total ~ treatment_assigned*int_var + 
                          child_age + 
                          person_time_at_risk + (1 | cohort:area),
                          data = new_model_data, family = binomial, nAGQ = 10,
                          control = glmerControl(optimizer = "bobyqa"))
#write_rds(itt_results_int, paste0(file_path, "Output/itt_pm_results_int_age.rds"))
save_summary <<- summary(itt_results_int)

@@

plot_results

@@

int_function(analysis_data, "home_sqft_2level")
n_table
save_contrasts
pm_summary_table
lrti_summary_table
save_summary
save_contrasts_full

@@

# Intent-to-treat framework, PM2.5 outcome

```{r, echo=TRUE}
# Run primary model and print results
itt_pm_results <- lmer(log(pm_mean_sampling_period) ~ treatment_assigned + 
                       (1 | cohort:area), data = analysis_data_winter1)
#write_rds(itt_pm_results, paste0(file_path, "Output/itt_pm_results.rds"))
# Adding the randomization variable for child_age leads to the exact same model results
# Adding a random term for home adversely impacts the model since there is only one
# distinct observation per home

@@

# Run primary model and print results
itt_pm_results_int <<- lmer(log(pm_mean_sampling_period) ~ treatment_assigned*int_var + 
                              child_age + 
                       (1 | cohort:area), data = new_model_data)
#write_rds(itt_pm_results_int, paste0(file_path, "Output/itt_pm_results_int_age.rds"))
save_summary <<- summary(itt_pm_results_int)

@@

plot_results

@@

int_function(analysis_data_winter1, "stove_grade_3level")
n_table
save_contrasts
pm_summary_table
lrti_summary_table
save_summary
save_contrasts_full

obs <- analysis_data_winter1 %>% 
  distinct(area, child_id_num, .keep_all = T) %>% 
  filter(!is.na(pm_mean_sampling_period)) %>% 
  filter(!is.na(child_age)) %>%
  filter(!is.na(area)) %>% 
  filter(!is.na(cohort)) %>% 
  filter(!is.na(treatment_assigned)) %>% 
  filter(!is.na(home_sqft_2level)) %>%
  group_by(home_sqft_2level, treatment_assigned) %>% 
  count()
obs

@@

#((exp(-.418)-1)*100)
```

@@

itt_pm_noak_results <- glmer(log(pm_mean_sampling_period) ~ treatment_assigned + child_age + 
                       (1 | cohort:area), data = analysis_data_noak)
write_rds(itt_pm_noak_results, paste0(file_path, "Output/itt_pm_noak_results.rds"))

itt_pm_at_home_results <- glmer(log(pm_mean_at_home_sampling_period) ~ treatment_assigned + 
                               child_age + (1 | cohort:area), 
                               data = analysis_data_winter1)
write_rds(itt_pm_at_home_results, paste0(file_path, "Output/itt_pm_at_home_results.rds"))

itt_pm_income_results <- glmer(log(pm_mean_sampling_period) ~ treatment_assigned + 
                               child_age + (1 | cohort:area) + 
                               income_3level, data = analysis_data_winter1)
write_rds(itt_pm_income_results, paste0(file_path, "Output/itt_pm_income_results.rds"))

itt_pm_filter_type_results <- glmer(log(pm_mean_sampling_period) ~ treatment_filter_type +
                                  child_age + (1 | cohort:area), data = analysis_data_winter1)
summary(itt_pm_filter_type_results)
tidy_results <- tidy(itt_pm_filter_type_results, conf.int = TRUE) %>% 
  mutate(group_filter = if_else(grepl("treatment", term), 1, 0)) %>% 
  filter(group_filter == 1) %>% 
  mutate(term = gsub("treatment_filter_type", "", term),
         model = "Filter type") %>% 
  mutate(estimate = round((exp(estimate)-1)*100, digits = 2),
         conf.low = round((exp(conf.low)-1)*100, digits = 2),
         conf.high = round((exp(conf.high)-1)*100, digits = 2)) %>% 
  dplyr::select(model, term, estimate, conf.low, conf.high)
tidy_results
table(model.frame(itt_pm_filter_type_results)$treatment_filter_type)
write_rds(itt_pm_filter_type_results, paste0(file_path, "Output/itt_pm_filter_type_results.rds"))

itt_pm_filter_comp_results <- glmer(log(pm_mean_sampling_period) ~ filter_compliance + 
                                  child_age + (1 | cohort:area), 
                                  data = analysis_data_winter1)
summary(itt_pm_filter_comp_results)
write_rds(itt_pm_filter_comp_results, paste0(file_path, "Output/itt_pm_filter_comp_results.rds"))

itt_pm_smoke_results <- glmer(log(pm_mean_sampling_period) ~ treatment_assigned + 
                              child_age + (1 | cohort:area) + 
                              residents_smoke, data = analysis_data_winter1)
write_rds(itt_pm_smoke_results, paste0(file_path, "Output/itt_pm_smoke_results.rds"))

itt_pm_burn_level_results <- glmer(log(pm_mean_sampling_period) ~ treatment_assigned + 
                                   child_age + (1 | cohort:area) + 
                                   burn_level_3level, data = analysis_data_winter1)
write_rds(itt_pm_burn_level_results, paste0(file_path, "Output/itt_pm_burn_level_results.rds"))

itt_pm_smoking_results <- glmer(log(pm_mean_sampling_period) ~ treatment_assigned + 
                                   child_age + (1 | cohort:area) + 
                                   home_act_smoking_sum, data = analysis_data_winter1)
write_rds(itt_pm_smoking_results, paste0(file_path, "Output/itt_pm_smoking_results.rds"))

itt_pm_windows_results <- glmer(log(pm_mean_sampling_period) ~ treatment_assigned + 
                                   child_age + (1 | cohort:area) + 
                                   home_act_windows_sum, data = analysis_data_winter1)
write_rds(itt_pm_windows_results, paste0(file_path, "Output/itt_pm_windows_results.rds"))

itt_pm_door_results <- glmer(log(pm_mean_sampling_period) ~ treatment_assigned + 
                                   child_age + (1 | cohort:area) + 
                                   home_act_door_sum, data = analysis_data_winter1)
write_rds(itt_pm_door_results, paste0(file_path, "Output/itt_pm_door_results.rds"))

itt_pm_sweep_results <- glmer(log(pm_mean_sampling_period) ~ treatment_assigned + 
                                   child_age + (1 | cohort:area) + 
                                   home_act_sweep_sum, data = analysis_data_winter1)
write_rds(itt_pm_sweep_results, paste0(file_path, "Output/itt_pm_sweep_results.rds"))

itt_pm_ambpm_results <- glmer(log(pm_mean_sampling_period) ~ treatment_assigned + 
                                   child_age + (1 | cohort:area) + 
                                   amb_pm_lrti, data = analysis_data_winter1)
write_rds(itt_pm_ambpm_results, paste0(file_path, "Output/itt_pm_ambpm_results.rds"))

itt_pm_ambtemp_results <- glmer(log(pm_mean_sampling_period) ~ treatment_assigned + 
                                   child_age + (1 | cohort:area) + 
                                   amb_temp_lrti, data = analysis_data_winter1)
write_rds(itt_pm_ambtemp_results, paste0(file_path, "Output/itt_pm_ambtemp_results.rds"))
```

```{r}
# Load results
itt_pm_results <- read_rds(paste0(file_path, "Output/itt_pm_results.rds"))
itt_pm_at_home_results <- read_rds(paste0(file_path, "Output/itt_pm_at_home_results.rds"))
itt_pm_noak_results <- read_rds(paste0(file_path, "Output/itt_pm_noak_results.rds"))
itt_pm_income_results <- read_rds(paste0(file_path, "Output/itt_pm_income_results.rds"))
itt_pm_filter_type_results <- read_rds(paste0(file_path, "Output/itt_pm_filter_type_results.rds"))
itt_pm_filter_comp_results <- read_rds(paste0(file_path, "Output/itt_pm_filter_comp_results.rds"))
itt_pm_smoke_results <- read_rds(paste0(file_path, "Output/itt_pm_smoke_results.rds"))
itt_pm_burn_level_results <- read_rds(paste0(file_path, "Output/itt_pm_burn_level_results.rds"))
itt_pm_smoking_results <- read_rds(paste0(file_path, "Output/itt_pm_smoking_results.rds"))
itt_pm_windows_results <- read_rds(paste0(file_path, "Output/itt_pm_windows_results.rds"))
itt_pm_door_results <- read_rds(paste0(file_path, "Output/itt_pm_door_results.rds"))
itt_pm_sweep_results <- read_rds(paste0(file_path, "Output/itt_pm_sweep_results.rds"))
itt_pm_ambpm_results <- read_rds(paste0(file_path, "Output/itt_pm_ambpm_results.rds"))
itt_pm_ambtemp_results <- read_rds(paste0(file_path, "Output/itt_pm_ambtemp_results.rds"))

@@

# Run results through function, save, combine for plotting
itt_pm_tidy <- results_function(itt_pm_results, "ITT Primary")
itt_pm_at_home_tidy <- results_function(itt_pm_at_home_results, "ITT PM at-home")
itt_pm_noak_tidy <- results_function(itt_pm_noak_results, "ITT no AK")
itt_pm_income_tidy <- results_function(itt_pm_income_results, "ITT + income")
#itt_pm_filter_type_tidy <- results_function(itt_pm_filter_type_results, "ITT filter type")
#itt_pm_filter_comp_tidy <- results_function(itt_pm_filter_comp_results, "ITT + filt comp")
itt_pm_smoke_tidy <- results_function(itt_pm_smoke_results, "ITT + smoke hx")
itt_pm_burn_level_tidy <- results_function(itt_pm_burn_level_results, "ITT + burn level")
itt_pm_smoking_tidy <- results_function(itt_pm_smoking_results, "ITT + smoke act")
itt_pm_windows_tidy <- results_function(itt_pm_windows_results, "ITT + window act")
itt_pm_door_tidy <- results_function(itt_pm_door_results, "ITT + door act")
itt_pm_sweep_tidy <- results_function(itt_pm_sweep_results, "ITT + sweep act")
itt_pm_ambpm_tidy <- results_function(itt_pm_ambpm_results, "ITT + amb PM")
itt_pm_ambtemp_tidy <- results_function(itt_pm_ambtemp_results, "ITT + amb temp")

# Combine cleaned results
itt_pm_results_combined <- rbind(itt_pm_tidy, itt_pm_at_home_tidy, itt_pm_noak_tidy, itt_pm_income_tidy, 
                              itt_pm_smoke_tidy, itt_pm_burn_level_tidy, itt_pm_smoking_tidy,
                              itt_pm_windows_tidy, itt_pm_door_tidy, itt_pm_sweep_tidy,
                              itt_pm_ambpm_tidy, itt_pm_ambtemp_tidy)

# Plot results
itt_pm_plot_estimates <- itt_pm_results_combined %>%
  mutate(model = factor(model,
                        levels = c("ITT Primary", "ITT PM at-home", "ITT no AK", "ITT + income", 
                                   "ITT + smoke hx", "ITT + burn level", "ITT + smoke act",
                                   "ITT + window act", "ITT + door act", "ITT + sweep act",
                                   "ITT + amb PM", "ITT + amb temp"))) %>% 
  ggplot(aes(group = term, shape = term)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  ggtitle(label = "Results for ITT framework, PM2.5 outcome") +
  labs(y = "% difference in PM2.5 \n compared to Control") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "top",
          legend.text = element_text(size = 14, colour = "black")) 
itt_pm_plot_estimates

@@

# Run primary model and print results
er_results_int <<- glmer(lrti_events_di_total ~ pm_mean_sampling_period_iqr*int_var + 
                          #child_age + 
                          gender + 
                          residents_smoke + 
                          race_parent + gender_parent +
                          income_3level + education_3level + 
                          amb_temp_lrti + amb_pm_lrti + 
                          person_time_at_risk +
                          (1 | home:cohort:area), 
                          data = new_model_data, family = binomial, nAGQ = 10,
                          control = glmerControl(optimizer = "bobyqa"))
#write_rds(itt_pm_results_int, paste0(file_path, "Output/itt_pm_results_int_age.rds"))
save_summary <<- summary(er_results_int)

@@

plot_results

@@

int_function(analysis_data, "child_age")
save_contrasts
pm_summary_table
lrti_summary_table
save_summary

@@

# Plot results
er_plot_estimates <- er_results_combined %>%
  mutate(model = factor(model,
                        levels = c("ER Primary", "ER PM at-home", "ER Winter 1 only", 
                                   "ER + burn level", "ER + home size", 
                                   "ER + stove grade", "ER + stove age"))) %>% 
  ggplot(aes(group = term, shape = term)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 1) +
  theme_bw() +  
  ggtitle(label = "Results for ER framework, LRTI outcome") +
  labs(y = "LRTI events per IQR \n increase in PM2.5") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "none",
          legend.text = element_text(size = 14, colour = "black")) 
er_plot_estimates

>>>>

---
title: 'KidsAIR: Main analysis'
author: "Ethan Walker"
date: "Updated 9 June 2021"
output: pdf_document
---

@@

```{r}
library(readxl)
library(naniar)
library(lubridate)
library(emmeans)
library(broom)
library(broom.mixed)
library(car)
library(zoo)
library(lme4)
library(lmerTest)
library(mctest)
library(tidyverse)
library(knitr)
library(kableExtra)
library(MASS)
library(faraway)
#library(DHARMa)
```

@@

analysis_data_winter1 <- read_rds(paste0(file_path, 
                                 "Output/kids_analysis_data_2obs_per_child.rds")) %>% 
  mutate(pm_mean_sampling_period_iqr = pm_mean_sampling_period/25,
         pm_mean_at_home_sampling_period_iqr = pm_at_home_sampling_period/25,
         pm_mean_at_home_sampling_period = pm_at_home_sampling_period,
         lrti_events_di_winter = as.factor(lrti_events_di_winter),
         child_age = factor(child_age, levels = c("< 1", "1+")),
         moisture_di = cut(moisture_closest, breaks = c(0, 11, 100),
                           labels = c("<11%", ">=11%")),
         stove_age_di = fct_collapse(stove_age_3level, 
                                     "0-5 years old" = "0-5 years old",
                                     "6+ years old" = c("6-15 years old", "16 + years old"),
                                     "Do not know" = "Do not know")) %>% 
  #filter(person_time_at_risk_winter > 0) %>% 
  #filter(area == "WMT") %>% 
  filter(winter_id == 1)

@@

# Run primary model and print results
itt_results_int <<- glmer(lrti_events_di_total ~ treatment_assigned*int_var + 
                          child_age + 
                          person_time_at_risk + (1 | home:cohort:area),
                          data = new_model_data, family = binomial, nAGQ = 10,
                          control = glmerControl(optimizer = "bobyqa"))
#write_rds(itt_results_int, paste0(file_path, "Output/itt_pm_results_int_age.rds"))
save_summary <<- summary(itt_results_int)

@@

plot_results 
Anova(itt_results_int)

@@

int_function(analysis_data, "residents_smoke")
n_table
save_contrasts
pm_summary_table
lrti_summary_table
save_summary
save_contrasts_full

@@

# Intent-to-treat framework, PM2.5 outcome
```{r}
# select distinct homes within datasets
winter_1_data_pm <- analysis_data_winter1 %>% 
  distinct(area, home, .keep_all = T)

winter_1_data_pm_noak <- winter_1_data_pm %>% 
  distinct(area, home, .keep_all = T) %>% 
  filter(area != "AK")
```

```{r, echo=TRUE}
# Run primary model and print results
itt_pm_results <- lmer(log(pm_mean_sampling_period) ~ treatment_assigned + 
                       (1 | cohort:area), data = winter_1_data_pm)
#write_rds(itt_pm_results, paste0(file_path, "Output/itt_pm_results.rds"))
# Adding the randomization variable for child_age leads to the exact same model results
# Adding a random term for home adversely impacts the model since there is only one
# distinct observation per home

@@

# Run primary model and print results
itt_pm_results_int <<- lmer(log(pm_mean_sampling_period) ~ treatment_assigned*int_var + 
                       (1 | cohort:area), data = new_model_data)
#write_rds(itt_pm_results_int, paste0(file_path, "Output/itt_pm_results_int_age.rds"))
save_summary <<- summary(itt_pm_results_int)

@@

plot_results 
Anova(itt_pm_results_int)

@@

int_function(winter_1_data_pm, "stove_grade_3level")

n_table
save_contrasts
pm_summary_table
lrti_summary_table
save_summary
save_contrasts_full

obs <- winter_1_data_pm %>% 
  distinct(area, child_id_num, .keep_all = T) %>% 
  filter(!is.na(pm_mean_sampling_period)) %>% 
  filter(!is.na(child_age)) %>%
  filter(!is.na(area)) %>% 
  filter(!is.na(cohort)) %>% 
  filter(!is.na(treatment_assigned)) %>% 
  filter(!is.na(stove_grade_3level)) %>%
  group_by(stove_grade_3level, treatment_assigned) %>% 
  count()
obs

@@

((exp(-0.07214)-1)*100)
```

@@

itt_pm_noak_results <- glmer(log(pm_mean_sampling_period) ~ treatment_assigned + 
                       (1 | cohort:area), data = winter_1_data_pm_noak)
summary(itt_pm_noak_results)
write_rds(itt_pm_noak_results, paste0(file_path, "Output/itt_pm_noak_results.rds"))

itt_pm_at_home_results <- glmer(log(pm_mean_at_home_sampling_period) ~ treatment_assigned + 
                               (1 | cohort:area), 
                               data = winter_1_data_pm)
write_rds(itt_pm_at_home_results, paste0(file_path, "Output/itt_pm_at_home_results.rds"))

itt_pm_income_results <- glmer(log(pm_mean_sampling_period) ~ treatment_assigned + 
                               (1 | cohort:area) + 
                               income_3level, data = winter_1_data_pm)
write_rds(itt_pm_income_results, paste0(file_path, "Output/itt_pm_income_results.rds"))

itt_pm_sqft_results <- glmer(log(pm_mean_sampling_period) ~ treatment_assigned + 
                               (1 | cohort:area) + 
                               home_sqft_2level, data = winter_1_data_pm)
write_rds(itt_pm_sqft_results, paste0(file_path, "Output/itt_pm_sqft_results.rds"))

itt_pm_filter_type_results <- glmer(log(pm_mean_sampling_period) ~ treatment_filter_type +
                                  (1 | cohort:area), data = winter_1_data_pm)
summary(itt_pm_filter_type_results)
tidy_results <- tidy(itt_pm_filter_type_results, conf.int = TRUE) %>% 
  mutate(group_filter = if_else(grepl("treatment", term), 1, 0)) %>% 
  filter(group_filter == 1) %>% 
  mutate(term = gsub("treatment_filter_type", "", term),
         model = "Filter type") %>% 
  mutate(estimate = round((exp(estimate)-1)*100, digits = 2),
         conf.low = round((exp(conf.low)-1)*100, digits = 2),
         conf.high = round((exp(conf.high)-1)*100, digits = 2)) %>% 
  dplyr::select(model, term, estimate, conf.low, conf.high)
tidy_results
table(model.frame(itt_pm_filter_type_results)$treatment_filter_type)
write_rds(itt_pm_filter_type_results, paste0(file_path, "Output/itt_pm_filter_type_results.rds"))

itt_pm_filter_comp_results <- glmer(log(pm_mean_sampling_period) ~ filter_compliance + 
                                  (1 | cohort:area), 
                                  data = winter_1_data_pm)
summary(itt_pm_filter_comp_results)
write_rds(itt_pm_filter_comp_results, paste0(file_path, "Output/itt_pm_filter_comp_results.rds"))

itt_pm_smoke_results <- glmer(log(pm_mean_sampling_period) ~ treatment_assigned + 
                              (1 | cohort:area) + 
                              residents_smoke, data = winter_1_data_pm)
write_rds(itt_pm_smoke_results, paste0(file_path, "Output/itt_pm_smoke_results.rds"))

itt_pm_burn_level_results <- glmer(log(pm_mean_sampling_period) ~ treatment_assigned + 
                                   (1 | cohort:area) + 
                                   burn_level_3level, data = winter_1_data_pm)
write_rds(itt_pm_burn_level_results, paste0(file_path, "Output/itt_pm_burn_level_results.rds"))

itt_pm_smoking_results <- glmer(log(pm_mean_sampling_period) ~ treatment_assigned + 
                                   (1 | cohort:area) + 
                                   home_act_smoking_sum, data = winter_1_data_pm)
write_rds(itt_pm_smoking_results, paste0(file_path, "Output/itt_pm_smoking_results.rds"))

itt_pm_windows_results <- glmer(log(pm_mean_sampling_period) ~ treatment_assigned + 
                                   (1 | cohort:area) + 
                                   home_act_windows_sum, data = winter_1_data_pm)
write_rds(itt_pm_windows_results, paste0(file_path, "Output/itt_pm_windows_results.rds"))

itt_pm_door_results <- glmer(log(pm_mean_sampling_period) ~ treatment_assigned + 
                                   (1 | cohort:area) + 
                                   home_act_door_sum, data = winter_1_data_pm)
write_rds(itt_pm_door_results, paste0(file_path, "Output/itt_pm_door_results.rds"))

itt_pm_sweep_results <- glmer(log(pm_mean_sampling_period) ~ treatment_assigned + 
                                   (1 | cohort:area) + 
                                   home_act_sweep_sum, data = winter_1_data_pm)
write_rds(itt_pm_sweep_results, paste0(file_path, "Output/itt_pm_sweep_results.rds"))

itt_pm_ambpm_results <- glmer(log(pm_mean_sampling_period) ~ treatment_assigned + 
                                   (1 | cohort:area) + 
                                   amb_pm_lrti, data = winter_1_data_pm)
write_rds(itt_pm_ambpm_results, paste0(file_path, "Output/itt_pm_ambpm_results.rds"))

itt_pm_ambtemp_results <- glmer(log(pm_mean_sampling_period) ~ treatment_assigned + 
                                   (1 | cohort:area) + 
                                   amb_temp_lrti, data = winter_1_data_pm)
write_rds(itt_pm_ambtemp_results, paste0(file_path, "Output/itt_pm_ambtemp_results.rds"))
```

```{r} 
# Load results
itt_pm_results <- read_rds(paste0(file_path, "Output/itt_pm_results.rds"))
itt_pm_at_home_results <- read_rds(paste0(file_path, "Output/itt_pm_at_home_results.rds"))
itt_pm_noak_results <- read_rds(paste0(file_path, "Output/itt_pm_noak_results.rds"))
itt_pm_income_results <- read_rds(paste0(file_path, "Output/itt_pm_income_results.rds"))
itt_pm_sqft_results <- read_rds(paste0(file_path, "Output/itt_pm_sqft_results.rds"))
itt_pm_filter_type_results <- read_rds(paste0(file_path, "Output/itt_pm_filter_type_results.rds"))
itt_pm_filter_comp_results <- read_rds(paste0(file_path, "Output/itt_pm_filter_comp_results.rds"))
itt_pm_smoke_results <- read_rds(paste0(file_path, "Output/itt_pm_smoke_results.rds"))
itt_pm_burn_level_results <- read_rds(paste0(file_path, "Output/itt_pm_burn_level_results.rds"))
itt_pm_smoking_results <- read_rds(paste0(file_path, "Output/itt_pm_smoking_results.rds"))
itt_pm_windows_results <- read_rds(paste0(file_path, "Output/itt_pm_windows_results.rds"))
itt_pm_door_results <- read_rds(paste0(file_path, "Output/itt_pm_door_results.rds"))
itt_pm_sweep_results <- read_rds(paste0(file_path, "Output/itt_pm_sweep_results.rds"))
itt_pm_ambpm_results <- read_rds(paste0(file_path, "Output/itt_pm_ambpm_results.rds"))
itt_pm_ambtemp_results <- read_rds(paste0(file_path, "Output/itt_pm_ambtemp_results.rds"))

@@

# Run results through function, save, combine for plotting
itt_pm_tidy <- results_function(itt_pm_results, "ITT Primary")
itt_pm_at_home_tidy <- results_function(itt_pm_at_home_results, "ITT PM at-home")
itt_pm_noak_tidy <- results_function(itt_pm_noak_results, "ITT no AK")
itt_pm_income_tidy <- results_function(itt_pm_income_results, "ITT + income")
itt_pm_sqft_tidy <- results_function(itt_pm_sqft_results, "ITT + home size")
#itt_pm_filter_type_tidy <- results_function(itt_pm_filter_type_results, "ITT filter type")
#itt_pm_filter_comp_tidy <- results_function(itt_pm_filter_comp_results, "ITT + filt comp")
itt_pm_smoke_tidy <- results_function(itt_pm_smoke_results, "ITT + smoke hx")
itt_pm_burn_level_tidy <- results_function(itt_pm_burn_level_results, "ITT + burn level")
itt_pm_smoking_tidy <- results_function(itt_pm_smoking_results, "ITT + smoke act")
itt_pm_windows_tidy <- results_function(itt_pm_windows_results, "ITT + window act")
itt_pm_door_tidy <- results_function(itt_pm_door_results, "ITT + door act")
itt_pm_sweep_tidy <- results_function(itt_pm_sweep_results, "ITT + sweep act")
itt_pm_ambpm_tidy <- results_function(itt_pm_ambpm_results, "ITT + amb PM")
itt_pm_ambtemp_tidy <- results_function(itt_pm_ambtemp_results, "ITT + amb temp")

# Combine cleaned results
itt_pm_results_combined <- rbind(itt_pm_tidy, itt_pm_at_home_tidy, itt_pm_noak_tidy, 
                                 itt_pm_income_tidy, itt_pm_sqft_tidy, 
                              itt_pm_smoke_tidy, itt_pm_burn_level_tidy, itt_pm_smoking_tidy,
                              itt_pm_windows_tidy, itt_pm_door_tidy, itt_pm_sweep_tidy,
                              itt_pm_ambpm_tidy, itt_pm_ambtemp_tidy)

# Plot results
itt_pm_plot_estimates <- itt_pm_results_combined %>%
  mutate(model = factor(model,
                        levels = c("ITT Primary", "ITT PM at-home", "ITT no AK", 
                                   "ITT + income", "ITT + home size",
                                   "ITT + smoke hx", "ITT + burn level", "ITT + smoke act",
                                   "ITT + window act", "ITT + door act", "ITT + sweep act",
                                   "ITT + amb PM", "ITT + amb temp"))) %>% 
  ggplot(aes(group = term, shape = term)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  ggtitle(label = "Results for ITT framework, PM2.5 outcome") +
  labs(y = "% difference in PM2.5 \n compared to Control") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "top",
          legend.text = element_text(size = 14, colour = "black")) 
itt_pm_plot_estimates

@@

# Run primary model and print results
er_results_int <<- glmer(lrti_events_di_total ~ pm_mean_sampling_period_iqr*int_var + 
                          child_age + 
                          gender + 
                          #residents_smoke + 
                          race_parent + gender_parent +
                          income_3level + education_3level + 
                          amb_temp_lrti + amb_pm_lrti + 
                          person_time_at_risk +
                          (1 | home:cohort:area), 
                          data = new_model_data, family = binomial, nAGQ = 10,
                          control = glmerControl(optimizer = "bobyqa"))
#write_rds(itt_pm_results_int, paste0(file_path, "Output/itt_pm_results_int_age.rds"))
save_summary <<- summary(er_results_int)

@@

plot_results 
Anova(er_results_int)

@@

int_function(analysis_data, "residents_smoke")
save_contrasts
pm_summary_table
lrti_summary_table
save_summary

@@

# Plot results
er_plot_estimates <- er_results_combined %>%
  mutate(model = factor(model,
                        levels = c("ER Primary", "ER PM at-home", "ER Winter 1 only", 
                                   "ER + burn level", "ER + home size", 
                                   "ER + stove grade", "ER + stove age"))) %>% 
  ggplot(aes(group = term, shape = term)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 1) +
  theme_bw() +  
  #ggtitle(label = "Results for ER framework, LRTI outcome") +
  labs(y = "Odds of LRTI per IQR \n increase in PM2.5") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "none",
          legend.text = element_text(size = 14, colour = "black")) 
er_plot_estimates
